Untitled

### 2024-01-09 resources/older manuscript versions/revision_notes.RMD
revision updates
finished tab3

Reviewer 2, comment 2: In the results the data were described in relation to % ou fold of changes. It is important to report the data also in absolute values.
 - Authors reply: Results chapter now updated with absolute values of change from baseline to post in both conditions
   - Glucose revision: Glucose ingestion before and after RT led to increases in plasma glucose levels compared to baseline by 38% immediately before RT (Figure 1B, 0 min: 2.05 ± 0.73 mmol/L), by 31% during RT (Figure 1B, 15 min: 1.75 ± 1.44 mmol/L) and by 32% immediately after RT (Figure 1B, 30 min: 1.62 ± 1.10 mmol/L, all : *p* \< 0.001), with no changes observed in the placebo condition (Figure 1B, 0 min: 0.09 ± 0.3 mmol/L, 15 min: 0.16 ± 0.35 mmol/L, 30 min: 0.18 ± 0.39 mmol/L, *p* \> 0.05). 
   - C-peptide revision: Glucose ingestion before and after RT led to increases in levels of c-peptide compared to baseline, by 95% immediately before (Figure 1C, 0 min: 796 ± 376.0 pmol/L) and 87% after RT (Figure 1C, 30 min: 793 ± 581.0 pmol/L, both *p* \< 0.001), with no changes observed with the placebo condition (Figure 1C, 0 min: 63.7 ± 71.0 pmol/L, 30 min: 53.9 ± 134.0 pmol/L, both *p* \> 0.05).
   - Strength index revision: Glucose ingestion before and after RT sessions did not generally improve skeletal muscle recovery throughout the intervention, neither during the intervention in a rested state (Figure 1D, 23hrs after exercise; Post 2RT: -0.02 ± 0.05 vs. -0.04 ± 0.03 *p* = `r pdiff.c2`, Post 4RT: -0.02 ± 0.05 vs. -0.06 ± 0.03 *p* = `r pdiff.c3`, glucose vs. placebo), nor acutely after the sixth and final RT-session (30min post 6RT: -0.03 ± 0.05 vs. -0.09 ± 0.06 *p* = `r pdiff.c5`, 2h post 6RT: -0.02 ± 0.07 vs. -0.08 ± 0.07 *p* = `r pdiff.c6`, glucose vs. placebo) or in a rested state after the sixth RT session (23h post 6RT: -0.05 ± 0.06 vs. -0.09 vs. 0.05 *p* = `r pdiff.c7`, glucose vs. placebo). Glucose ingestion before and after RT compared to placebo was associated with a 7% less reduction in strength after five RT sessions (Figure 1D, -0.06 ± 0.06 vs -0.14 ± 0.12 *p* = `r pdiff.c4`, glucose vs. placebo).
   - Total RNA and rRNA revision:

@@

Reviewer 2, comment 6: In Table 1, provide body fat percentage data, together with the absolute lean mass data (already shown), they become more informative to the reader.
 - Må hente ut denne dataen

>>>>

Reviewer 2, comment 2: In the results the data were described in relation to % ou fold of changes. It is important to report the data also in absolute values.
 - Authors reply: Results chapter now updated with absolute values of change from baseline to post in both conditions
   - Glucose revision: Glucose ingestion before and after RT led to increases in plasma glucose levels compared to baseline by 38% immediately before RT (Figure 1B, 0 min: 2.05 ± 0.73 mmol/L), by 31% during RT (Figure 1B, 15 min: 1.75 ± 1.44 mmol/L) and by 32% immediately after RT (Figure 1B, 30 min: 1.62 ± 1.10 mmol/L, all : *p* \< 0.001), with no changes observed in the placebo condition (Figure 1B, 0 min: 0.09 ± 0.3 mmol/L, 15 min: 0.16 ± 0.35 mmol/L, 30 min: 0.18 ± 0.39 mmol/L, *p* \> 0.05). 
   - C-peptide revision: Glucose ingestion before and after RT led to increases in levels of c-peptide compared to baseline, by 95% immediately before (Figure 1C, 0 min: 796 ± 376.0 pmol/L) and 87% after RT (Figure 1C, 30 min: 793 ± 581.0 pmol/L, both *p* \< 0.001), with no changes observed with the placebo condition (Figure 1C, 0 min: 63.7 ± 71.0 pmol/L, 30 min: 53.9 ± 134.0 pmol/L, both *p* \> 0.05).
   - Absolute values for humac added in a table (tab3), reference by "Table 3 shows the mean change in absolute peak torque values per condition and angular velocity." at the end of the strength index results.
   - western/rna??Prøve å inkludere rådata i figurene?

@@

Reviewer 2, comment 6: In Table 1, provide body fat percentage data, together with the absolute lean mass data (already shown), they become more informative to the reader.
 - Må hente ut denne dataen. Tabellen er oppdatert med tilfeldige tall for kroppsfett som "placeholder". Trenger bare å plotte inn rett data i dxa arket.
